Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
add before and after for private inner class

@@

>>>>

And:
\begin{lstlisting}[style=stainless]
  [Warning ] number/NumberType.scala:59:3: Could not extract tree in class: case private class Int64Impl extends Int64 with Product with Serializable {
    [Warning ]   <caseaccessor> <paramaccessor> private[this] val underlying: BigInt = _;
    [Warning ]   <stable> <caseaccessor> <accessor> <paramaccessor> def underlying: BigInt = Int64Impl.this.underlying;
    [Warning ]   def <init>(underlying: BigInt): addition.modified.number.Int64.Int64Impl = {
    [Warning ]     Int64Impl.super.<init>();
    [Warning ]     ()
    [Warning ]   };
    [Warning ]   scala.this.Predef.require(Int64Impl.this.underlying.>=(math.this.BigInt.long2bigInt(-9223372036854775808L)), "Number was too small for a int64, got: ".+(Int64Impl.this.underlying));
    [Warning ]   scala.this.Predef.require(Int64Impl.this.underlying.<=(math.this.BigInt.long2bigInt(9223372036854775807L)), "Number was too big for a int64, got: ".+(Int64Impl.this.underlying));
    [Warning ]   <synthetic> def copy(underlying: BigInt = underlying): addition.modified.number.Int64.Int64Impl = new Int64Impl(underlying);
    [Warning ]   <synthetic> def copy$default$1: BigInt = Int64Impl.this.underlying;
    [Warning ]   override <synthetic> def productPrefix: String = "Int64Impl";
    [Warning ]   <synthetic> def productArity: Int = 1;
    [Warning ]   <synthetic> def productElement(x$1: Int): Any = x$1 match {
    [Warning ]     case 0 => Int64Impl.this.underlying
    [Warning ]     case _ => throw new IndexOutOfBoundsException(x$1.toString())
    [Warning ]   };
    [Warning ]   override <synthetic> def productIterator: Iterator[Any] = runtime.this.ScalaRunTime.typedProductIterator[Any](Int64Impl.this);
    [Warning ]   <synthetic> def canEqual(x$1: Any): Boolean = x$1.$isInstanceOf[addition.modified.number.Int64.Int64Impl]();
    [Warning ]   override <synthetic> def hashCode(): Int = ScalaRunTime.this._hashCode(Int64Impl.this);
    [Warning ]   override <synthetic> def toString(): String = ScalaRunTime.this._toString(Int64Impl.this);
    [Warning ]   override <synthetic> def equals(x$1: Any): Boolean = Int64Impl.this.eq(x$1.asInstanceOf[Object]).||(x$1 match {
    [Warning ]   case (_: addition.modified.number.Int64.Int64Impl) => true
    [Warning ]   case _ => false
    [Warning ] }.&&({
    [Warning ]     <synthetic> val Int64Impl$1: addition.modified.number.Int64.Int64Impl = x$1.asInstanceOf[addition.modified.number.Int64.Int64Impl];
    [Warning ]     Int64Impl.this.underlying.==(Int64Impl$1.underlying).&&(Int64Impl$1.canEqual(Int64Impl.this))
    [Warning ]   }))
    [Warning ] } (class scala.reflect.internal.Trees$ClassDef)
                 private case class Int64Impl(underlying: BigInt) extends Int64 {
                 ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
\end{lstlisting}

@@

And before:
\begin{lstlisting}[style=scala]
case object Int64 extends BaseNumbers[Int64] {
  private case class Int64Impl(underlying: BigInt) extends Int64 {
    require(underlying >= -9223372036854775808L,
      "Number was too small for a int64, got: " + underlying)
    require(underlying <= 9223372036854775807L,
      "Number was too big for a int64, got: " + underlying)
  }

  lazy val zero = Int64(0)
  lazy val one = Int64(1)

  lazy val min = Int64(-9223372036854775808L)
  lazy val max = Int64(9223372036854775807L)

  def apply(long: Long): Int64 = Int64(BigInt(long))

  def apply(bigInt: BigInt): Int64 = Int64Impl(bigInt)
}
\end{lstlisting}

After:
\begin{lstlisting}[style=scala]
case object Int64 extends BaseNumbers[Int64] {
  lazy val zero = Int64(0)
  lazy val one = Int64(1)

  lazy val min = Int64(-9223372036854775808L)
  lazy val max = Int64(9223372036854775807L)

  def apply(long: Long): Int64 = Int64(BigInt(long))

  def apply(bigInt: BigInt): Int64 = Int64Impl(bigInt)
}

private case class Int64Impl(underlying: BigInt) extends Int64 {
  require(underlying >= -9223372036854775808L,
    "Number was too small for a int64, got: " + underlying)
  require(underlying <= 9223372036854775807L,
    "Number was too big for a int64, got: " + underlying)
}
\end{lstlisting}
